Parametricity Consequences of GADTs Representations

### 2021-02-16 20-gadts/GADT-story.tex
setting up Par section for Enrico

The key idea underlying Reynolds' parametricity is to give each type
$F(\alpha)$ with one free variable $\alpha$ a {\em set interpretation}
$F_0$ taking sets to sets and a \emph{relational interpretation} $F_1$
taking relations $R : \rel(A,B)$ to relations $F_1 (R) : \rel(F_0 (A),
F_0 (B))$, and to interpret each term $t(\alpha,x) : F(\alpha)$ with
one free term variable $x : G(\alpha)$ as a map $t_0$ associating to
each set $A$ a function $t_0(A) : G_0(A) \to F_0(A)$. These
interpretations are given inductively on the structures of $F$ and $t$
in such a way that they imply two fundamental theorems. The first is
an \emph{Identity Extension Lemma}, which states that $F_1(\Eq_A) =
\Eq_{F_0(A)}$, and is the essential property that makes a model
relationally parametric rather than just induced by a logical
relation. The second is an \emph{Abstraction Theorem}, which states
that, for any $R :\rel(A, B)$, $(t_0(A),t_0(B))$ is a morphism in
$\rel$ from $(G_0(A),G_0(B),G_1(R))$ to $(F_0(A),F_0(B),F_1(R))$. The
Identity Extension Lemma is similar to the Abstraction Theorem except
that it holds for {\em all} elements of a type's interpretation, not
just those that interpret terms.  Similar theorems are required for
types and terms with any number of free variables.

>>>>

{\color{red} This might not be relevant, since we only care about the
  fibredness.} 
The key idea underlying Reynolds' parametricity is to give each type
$F(\alpha)$ with one free variable $\alpha$ a {\em set interpretation}
$F_0$ taking sets to sets and a \emph{relational interpretation} $F_1$
taking relations $R : \rel(A,B)$ to relations $F_1 (R) : \rel(F_0 (A),
F_0 (B))$, and to interpret each term $t(\alpha,x) : F(\alpha)$ with
one free term variable $x : G(\alpha)$ as a map $t_0$ associating to
each set $A$ a function $t_0(A) : G_0(A) \to F_0(A)$. These
interpretations are given inductively on the structures of $F$ and $t$
in such a way that they imply two fundamental theorems. The first is
an \emph{Identity Extension Lemma}, which states that $F_1(\Eq_A) =
\Eq_{F_0(A)}$, and is the essential property that makes a model
relationally parametric rather than just induced by a logical
relation. The second is an \emph{Abstraction Theorem}, which states
that, for any $R :\rel(A, B)$, $(t_0(A),t_0(B))$ is a morphism in
$\rel$ from $(G_0(A),G_0(B),G_1(R))$ to $(F_0(A),F_0(B),F_1(R))$. The
Identity Extension Lemma is similar to the Abstraction Theorem except
that it holds for {\em all} elements of a type's interpretation, not
just those that interpret terms.  Similar theorems are required for
types and terms with any number of free variables.
